Improving Models to Predict Holocellulose and Klason Lignin Contents for Peat Soil Organic Matter with Mid Infrared Spectra

### 2022-03-07 README.Rmd
Add funding information.

[![DOI](https://zenodo.org/badge/465653387.svg)](https://zenodo.org/badge/latestdoi/465653387)

@@

>>>>

[![DOI](https://zenodo.org/badge/465653387.svg)](https://zenodo.org/badge/latestdoi/465653387) ![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)

@@

### Funding

This study was funded by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) grant no. KN 929/23-1 to Klaus-Holger Knorr and grant no. PE 1632/18-1 to Edzer Pebesma. We acknowledge support from the Open Access Publication Fund of the University of Münster.

### 2022-03-07 analysis/paper/001-paper-main.Rmd
Add DOI for zenodo upload.
Add funding information.

    Data and code to reproduce our analyzes are available via [---todo: add link].

@@

  We like to thank @Hodgkins.2018 and @DelaCruz.2016 for provision of data and code to reproduce and modify their analyses, and @Allaire.2020 for provision of an Rmarkdown template. We thank Suzanne Hodgkins and Jeff Chanton for constructive discussions which helped to improve a first version of this manuscript. We acknowledge support from the Open Access Publication Fund of the University of Münster.

>>>>

    Data and code to reproduce our analyses are available via <https://doi.org/10.5281/zenodo.6325760>.

@@

  We like to thank @Hodgkins.2018 and @DelaCruz.2016 for provision of data and code to reproduce and modify their analyses, and @Allaire.2020 for provision of an Rmarkdown template. We thank Suzanne Hodgkins and Jeff Chanton for constructive discussions which helped to improve a first version of this manuscript. This study was funded by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) grant no. KN 929/23-1 to Klaus-Holger Knorr and grant no. PE 1632/18-1 to Edzer Pebesma. We acknowledge support from the Open Access Publication Fund of the University of Münster.
